\documentclass[a4paper,10pt]{article}
\usepackage[a4paper,margin=1in,footskip=0.25in]{geometry}

\usepackage{marvosym}
\usepackage{fontspec}
\usepackage{xunicode,xltxtra,url,parskip}
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[big]{layaureo} 
\usepackage{supertabular}
\usepackage{titlesec}

\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}


\defaultfontfeatures{Mapping=tex-text}

\setmainfont[
BoldFont = Roboto-Light.otf,
ItalicFont = Roboto-LightItalic.otf
]
{Roboto-Thin.ttf}


\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}

\hyphenation{im-pre-se}

\begin{document}

\pagestyle{empty} 

\font\fb=''[cmr10]'' 

\par{\centering
		{\Huge Robert \textsc{McConnell}
	}\bigskip\par}

\par{\centering
    robert.mcconnell3@mail.dcu.ie \\
    github.com/AlbertFaust \\ 
    albertfaust.com \\
}\bigskip\par
\par{\centering
I am currently studying Electronic and Computer Engineering in Dublin City University. \\
I am passionate about technology, fixing broken things and learning. \\
}\bigskip\par
\section{\textbf{Education}}

\begin{tabular}{r|p{11cm}}
 \emph & Dublin City University \\\textsc{2014-Present}&\emph{Electronic and Computer Engineering}\\\multicolumn{2}{c}{} \\
\emph & Belvedere College SJ \\\textsc{2008-2014}&\emph{Secondary Level Education}\\
\end{tabular}

\section{\textbf{Experience}}
\begin{tabular}{rl}	
\textsc{Summer} 2015 & \textbf{Intern, Performance Engineering Laboratory} - Dublin City University, Dublin.\\
& Built a new website using HTML, CSS and Javascript with the Bootstrap \\
& framework under the supervision of Dr. Gabriel Miro Muntean \\
& for the Performance Engineering Laboratory.
Improved the design and user \\
& experience of the site by restructuring the navigation and updating the \\
& outdated style using the scrollspy.js Bootstrap plugin and some Javascript. The \\
& new site is also responsive to different screen resoloutions unlike the old site.\\&\\

\textsc{Summer} 2015 & \textbf{Technician, Compliance Engineering Ireland} - Dunshaughlin , Meath.\\
& In CEI I was exposed to different types of EMC testing and learned a lot about them. \\
& I worked along side experienced engineers who were able to teach me how the \\
& products we were testing worked and to ensure they met the standards for each \\
& test. Some of the tests I performed include radio emissions, radio immunity, \\
& conduction emissions, static testing and radio tests. It allowed me to understand \\
& how electronics work in a practical setting and I gained huge insight into EMC.\\&\\

\textsc{February} 2012 & \textbf{Intern, Graffiti Design} - Fairview , Dublin.\\
& During my time in Graffiti Design I assisted in the backing up of their databases\\
& after a computer crash. It provided valuable technical experience and showed \\
& me how to work in a constantly changing environment that lacked usual\\
& business structure.\\&\\
\end{tabular}

\section{\textbf{Accomplishments/Interests}}
\begin{itemize}
  \item Experience in C/C++ and Java. (Software Development - Class rank: 1 of 170, Grade: 95\%) 
  \item Comfortable with various Linux distributions.
  \item First Year Representative of Redbrick, DCU’s Computer Networking Society.
  \item Mentor in DCU CoderDojo teaching programming to kids and volunteered at events such as Coolest Projects.
  \item Helped organise and participated in the Belvedere Sleep Out two times and also made the \\ website for the events and donations. \end{itemize}

\section{\textbf{Projects}}
\emph{Wallpaper to Theme} - Java\\
A program that generates a terminal colour scheme from a wallpaper.
\begin{itemize}
  \item Implements 'Lloyd's Algorithm' and 'K-Means Clustering' to determine the most dominant colours in the image.\end{itemize}
  \emph{Gravity Assist Simulator} - C++/OpenGl \emph{[Work in Progress]}\\ 
A gravity assist (slingshot) simulator written in C++ and using OpenGl. 
\begin{itemize}
  \item Will use 'real physics' applying Kepler's Laws and Newtonian Gravitation. \end{itemize}
\par{\centering
\emph{My other projects can be seen on my GitHub at github.com/AlbertFaust} \\
}
\section{\textbf{References}}
Available upon request.
\end{document}
